---
title: "BBets Project"
author: "Logan Martinez"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is won/lost on a bet that at least two people have the same b'day in a class of 35.  Instructor wagers 2:1 

Instuctor has done this 15 times,  
1.what is his expected win/loss amount,  
2. how much would the instructor have to wager to make the bet fair?  
3. how many students would have to be in the class for a 2:1 bet to be fair?   
 
 
```{r}
days = 1:365

nStudents = 35
nBets = nStudents*15

saveArray=vector('numeric')
for(k in 1:1000){
  bank = 0
  for(i in 1:nBets){
    sampleClass = sample(days, nStudents, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == nStudents) bank = bank -4.35
    else bank = bank + 1
  }
saveArray[k]= bank
}

```
 
histogram of bank amounts.   

```{r}
hist(saveArray)
```

Answer questions #1

```{r}
print('average amt:')
print(mean(saveArray))
```

1. The amt of $ on average won/lost is 233 for Dr. J. 
  
2. The amt of $ Dr. J should wager to have it be even is $4.35

3. The number of students to break even at 2:1 is 29 students. That puts it at 18.5. With 28 students it goes into the negatives. 
  
  